Supporting 10 common mistakes article

### 2025-08-29 example.Rmd
thread control

suppressPackageStartupMessages({
  library("getDEE2")
  library("DESeq2")
  library("kableExtra")
  library("clusterProfiler")
  library("fgsea")
  library("eulerr")
  library("gplots")
})

@@

sessionInfo()

>>>>

suppressPackageStartupMessages({
  library("getDEE2")
  library("DESeq2")
  library("kableExtra")
  library("clusterProfiler")
  library("fgsea")
  library("eulerr")
  library("gplots")
  library("RhpcBLASctl")
})

RhpcBLASctl::blas_set_num_threads(1)

@@

save.image("example.Rdata")
sessionInfo()

### 2025-08-29 example_10m.Rmd
thread control

@@

suppressPackageStartupMessages({
  library("getDEE2")
  library("DESeq2")
  library("kableExtra")
  library("clusterProfiler")
  library("eulerr")
  library("gplots")
  library("mitch")
})

>>>>

suppressPackageStartupMessages({
  library("getDEE2")
  library("DESeq2")
  library("kableExtra")
  library("clusterProfiler")
  library("eulerr")
  library("gplots")
  library("mitch")
  library("RhpcBLASctl")
})

@@
